\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2012-10-31 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
updates the user manual

point source located exactly at a grid point instead of a \texttt{CMTSOLUTION} moment-tensor source. 
When the force source does not fall exactly at a \texttt{GLL} point, the solver interpolates the force between grid points 

@@

Normally, if a \texttt{CMTSOLUTION} moment-tensor source is used, a (pseudo) Heaviside step 
function with a very short half duration is used for elastic cases to represent the permanent slip on the fault while 
in the acoustic case a Gaussian source time function with a similarly short half duration is used to physically describe 
actions within the fluid. Similarly, if a \texttt{FORCESOLUTION} force source is used, we need a source time function 
with finite support, so a (pseudo) Dirac delta source time function (which is actually a Gaussian of very
short half duration, i.e. hdur = 5 * DT) is used by default.
Any other source-time function may then be obtained by convolution.

@@

\begin{itemize}
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item Set the \texttt{half duration} parameter of the Ricker source
  time function when {\texttt{USE\_RICKER\_TIME\_FUNCTION}} is turned
  on in the main parameter file {\texttt{Par\_file}}. In the case the
  solver uses a (pseudo) Dirac delta source time function to represent
  a force point source, a very short \texttt{half duration} parameter
  (hdur = 5 * DT) is automatically set by default.
\item Set the latitude, longitude, depth of the source in geographical
  coordinates.
\item Set the magnitude of the force source.
\item Set the components of a (non-unitary) direction vector for the
  force source in the East/North/Vertical basis (see Appendix A for
  the orientation of the reference frame).
\end{itemize}

>>>>

point source instead of a \texttt{CMTSOLUTION} moment-tensor source. 
When the force source does not fall exactly at a grid point, the solver interpolates the force between grid points 

@@

Originally, if a \texttt{CMTSOLUTION} moment-tensor source is used, a (pseudo) Heaviside step 
function with a very short half duration is defined for elastic cases to represent the permanent slip on the fault while 
in the acoustic case a Gaussian source time function with a similarly short half duration is defined to physically describe 
actions within the fluid. Otherwise, if a \texttt{FORCESOLUTION} force source is used, a (pseudo) Dirac delta source time 
function is defined by default. Any other source-time function may then be obtained by convolution.

@@

\begin{itemize}
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item Set the \texttt{half duration} parameter of the Ricker source
  time function when {\texttt{USE\_RICKER\_TIME\_FUNCTION}} is turned
  on in the main parameter file {\texttt{Par\_file}}. In case that the
  solver uses a (pseudo) Dirac delta source time function to represent
  a force point source, a very short \texttt{half duration} parameter
  (hdur = 5 * DT) is automatically set by default.
\item Set the latitude, longitude, depth of the source in geographical
  coordinates.
\item Set the magnitude of the force source.
\item Set the components of a (non-unitary) direction vector for the
  force source in the East/North/Vertical basis (see Appendix A for
  the orientation of the reference frame).
\end{itemize}
